Argennon: A Scalable Smart Contract Platform

### 2021-07-12 tex/sections/elements.tex
Use HTTP for smart contracts
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every Argennon transaction consists of two \texttt{i\_invoke\_dispatcher} instructions, the first instruction always
transfers the proposed fee of the transaction in ARG from a sender account to the fee sink accounts, and
the second performs the requested operation.

Users interact with AVM smart contracts using
the second \texttt{i\_invoke\_dispatcher} instruction of a transaction,
Transferring all assets, including ARG, is done by that instruction.

Argennon transactions do not have a sender. The authorization of the requested operation is always done by checking the
digital signatures that are provided as a part of the argument list to the root smart contract method.

@@

>>>>

Every Argennon transaction consists of two \texttt{i\_invoke\_dispatcher} instructions, the first instruction always
transfers the proposed fee of the transaction in ARGs from a sender account to the fee sink accounts, and
the second performs the requested operation. If the first instruction fails, the transaction will not be added to
the Argennon blockchain.

Users interact with AVM smart contracts using
the second \texttt{i\_invoke\_dispatcher} instruction of a transaction.
Transferring all assets, including ARG, is done by that instruction.

The \texttt{i\_invoke\_dispatcher} instruction invokes the \texttt{dispatcher} method of a smart contract. Every AVM
smart contract has a \texttt{dispatcher} method, and the Argennon protocol requires
the \texttt{dispatcher} method to accept an HTTP request as its argument and
return an HTTP response.

As a result, every Argennon transaction contains two HTTP requests. In addition to these HTTP requests, the
transaction is required to contain a resource declaration object, specifying the maximum amount of resources
it needs for execution.

\note{Argennon smart contracts use HTTP as the application protocol and they are advised to have a RESTful API design.}

@@

Argennon transactions do not have a sender. The authorization of the requested operation is always done by checking the
digital signatures that are provided as a part of the HTTP request to the \texttt{dispatcher} method.
